---
fomat: 
  html:
    theme: cosmo
---

## Completed deliverables

- [**Deliverable 2.1**](resources/deliverables/deliverable_2.1.pdf){target="_blank"} - Exploration of AI-ML through citizen science approaches.
- [**Deliverable 11.1**](resources/deliverables/deliverable_11.1.pdf){target="_blank"} - Report describing the training and test sets.
- [**Deliverable 9.1**](resources/deliverables/deliverable_9.1.pdf){target="_blank"} - Methodological aspects for early imputation in the production of official statistics

## List of Project Deliverables

[*See interactive deliverable tracker here*](https://aiml4os.shinyapps.io/project_tracker){target="_blank"}

```{r , echo=F  }

deliv <- readRDS('resources/rds_files/deliv_data.rds')
names(deliv) <- c('Description', 'Organisation', 'Workpackage', 'ID' , 'Title' , 'Due Date')
deliv$Workpackage <- as.character(deliv$Workpackage )
deliv$Workpackage <- factor(deliv$Workpackage, levels = as.character(1:13))
deliv$Organisation <- factor(deliv$Organisation)

names(deliv)[names(deliv) == 'Workpackage'] <- 'WP'
names(deliv)[names(deliv) == 'Organisation'] <- 'Org.'

DT::datatable(deliv ,
              filter = 'top',
              rownames = F,
              options = list(
                pageLength = 5,
                autoWidth = TRUE,
                    responsive = TRUE,
                    columnDefs = list(
                      list(width = "35%", targets = 0),
                      list(width = "10%", targets = 1),
                      list(width = "10%", targets = 2),
                      list(width = "10%", targets = 3),
                      list(width = "20%", targets = 4),
                      list(width = "15%", targets = 5)
                    )
                ))
```

## List of Project Tasks

```{r , echo=F  }

tasks <- readRDS('resources/rds_files/task_data.rds')
names(tasks) <- c('Workpackage', 'ID' , 'Start Date' , 'End Date', 'Description')
tasks <- tasks[ , c('Description','Workpackage', 'ID' , 'Start Date' , 'End Date')]
tasks$Workpackage <- as.character(tasks$Workpackage)
tasks$Workpackage <- factor(tasks$Workpackage, levels = as.character(1:13))

names(tasks)[names(tasks) == 'Workpackage'] <- 'WP'

DT::datatable(tasks ,
              filter = 'top',
              rownames = F,
              options = list(
                pageLength = 5,
                autoWidth = TRUE,
                    responsive = TRUE,
                    columnDefs = list(
                      list(width = "50%", targets = 0),
                      list(width = "10%", targets = 1),
                      list(width = "10%", targets = 2),
                      list(width = "15%", targets = 3),
                      list(width = "15%", targets = 4)
                    )
                ))
```

<br>
